\cvletter{}

\cvparagraph{}
  {My name is Oriol Mirosa, and I am applying for the position of [data scientist] with [company name] as advertised on [Indeed.com].}
\cvparagraph{}
  {For the last fifteen years I have been engaged in research 

   in academic environments, most recently as an Assistant Professor of Sociology and Global Studies at the University of Wisconsin-Milwaukee. During this time, I have learnt to ask questions and answer them with data, both quantitative and qualitative. I have received extensive training in statistics, and I have employed machine learning and visualization tools in order to best identify patterns and communicate my findings. I have several academic publications and I have presented numerous times at conferences and workshops. I believe that this training and experience make me an ideal candidate for the data science position at your company. Although I do not have a background in computer science and engineering, I have worked hard to learn to code and become proficient in the use of linear algebra and programming languages such as R and Python. I also believe that training in the social sciences gives me an ability to understand the complex social processes that underpin the operations of firms such as [company name]. This is also something that I learnt in my M.B.A. studies and in my early consulting work.}
\cvparagraph{}
  {I am particularly excited about the possibility of working at [company name]. I have spent the last five years in a global studies academic position, which means that I have thought deeply about the challenges of acting in a globalized world. The insights that I have gained from this process make me a valuable asset for a company of global reach such as [company name]. I believe that data science opens opportunities for improvement beyond the mere calculation of basic business data. It allows us to better understand customers and suppliers, our relationships with them, and the ways in which we can anticipate trends and find innovative strategies to face them. I would be honor to contribute to this process at [company name].}
\cvparagraph{}
  {Please find my contact information at the top of this letter, as well as on my enclosed resume. I appreciate your time spent reading this letter, and I look forward to hearing from you soon.}
